Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-05-24 writeup/gz_hubble_data.tex
Legends on all subfigures of comparisons
PNG -> PDF for comparisons

Comparisons tweak
non-breaking spaces in text

\item The Great Observatories Origins Deep Survey \citep[GOODS;][]{gia04}
    covered two separate fields in the northern and southern hemispheres: the Hubble
    Deep Field-North ($\alpha=12^\textrm{h}36^\textrm{m},
    \delta=+62^\circ14^\prime$) and the Chandra Deep Field-South
    ($\alpha=03^\textrm{h}32^\textrm{m}, \delta=-27^\circ48^\prime$). The \hst{}
    ACS imaging data from the two fields are referred to as GOODS-N and GOODS-S,
    respectively. ACS imaging in GOODS fields used 4 filters -- F435W (\Bband),
    \Vband, F775W (\iband), and F850LP (\zband). The mean exposure times for each
    epoch varied by band, from 1050--2100~seconds. The \Bband{} images were completed
    in a single epoch at the beginning of the survey, but the \Vband, \iband, and
    \zband{} images were taken in five separate epochs separated by 40--50~days
    each. Images were dithered to a pixel scale of 0.03~\arcsec/pixel and covered a
    total area of $\sim320$~arcmin$^2$ (160~arcmin$^2$ per north/south field). The
    $5\sigma$ limiting magnitude for extended sources was 25.7 for \Vband{} and
    25.0 for \iband.

\item The Cosmic Evolution Survey \citep[COSMOS;][]{sco07} covered an area of
    $\sim1.8$~deg$^2$ centered at $\alpha=10^\textrm{h}00^\textrm{m},
    \delta=+02^\circ12^\prime$. Its location near the celestial equator was
    designed to enable coverage by ground-based telescopes in both the Northern and
    Southern Hemispheres, in addition to space-based observatories. The ACS data
    for COSMOS consisted of 1~orbit per pointing with an exposure time of
    2028~seconds in \Iband; 590 total pointings were used to cover the entire
    field. The image resolution was dithered to 0.05~\arcsec/pixel. The 50\%
    completeness magnitude for a galaxy with a half-light radius of
    $0.50^{\prime\prime}$ in \Iband{} was 24.7 mag.

\item The Galaxy Evolution from Morphologies and SEDs
    \citep[GEMS;][]{rix04,cal08} survey was also centered on the Chandra Deep
    Field-South. The GEMS data covered $\sim800$~arcmin$^2$, completely surrounding
    the area covered by GOODS-S. Images from ACS in GEMS had 1 orbit per pointing
    for a total of 63~pointings. The exposure times were 2160 and 2286~seconds in
    \Vband{} and \zband{}, respectively. The image resolution had a pixel scale
    of 0.03~\arcsec/pixel. The $5\sigma$ limiting magnitude for source
    detection was 25.7 AB in \Vband{} and 24.2~AB in \zband.

@@

%The creation of 51,861 images from these sources is described in Section
%\ref{ssec:galselect} below.
Single-epoch images from SDSS Stripe~82 were selected using the criteria
from \citet{wil13}, which required limits of \texttt{petroR90\_r}$ >
3$\arcsec~(where \texttt{petroR90\_r} is the radius containing 90\% of the
$r^\prime$ Petrosian flux) and a magnitude brighter than $m_r < 17.77$. The
images used were three-color composites created using the $g^\prime$, $r^\prime$, and
$i^\prime$ filters \citep{nie04}. 21,522 galaxies in SDSS met these criteria.
Co-added images from Stripe~82 were selected from the union of galaxies with
co-added magnitudes brighter than $17.77$~mag, and the galaxies detected in the
\stripe{} images and matched to a co-add source. This resulted in a total
set of 30,339 images. Of the images in the co-added sample, 5144 (17~percent)
were dimmer than the initial magnitude cut of 17.77.

@@

Two sets of simulated AGN were generated in GZH. The first set (version~1) was
assembled from 95~galaxies from GOODS-S imaging and empirical PSFs made by
combining stars in the GOODS fields using the PSF creation tools in
\texttt{daophot}.  The second set (version~2) was assembled from 96~galaxies in
GOODS-S; this version used simulated PSFs from \texttt{TinyTim} \citep{kri93},
drizzled using the same procedures as those used in the reduction of the GOODS-S
images \citep{koe02,koe03,gia04}. The use of these 2 versions facilitates
comparisons between these different PSF creation methods, which are widely used
in AGN host galaxy morphology studies
\citep[e.g.,][]{san04,sim08,pie10a,simm11}.  Each PSF creation method has
advantages and disadvantages: the empirical PSFs better represent the nuances
of the PSF in the specific data being used and look more realistic at lower
luminosities, but the extended features of the noiseless \texttt{TinyTim} PSFs
are visually more realistic at higher luminosities.
% okay so I'm a cheeky self-citing biyotch

@@

The dimming and resolution effects of redshift can significantly affect galaxy
classifications derived from any method. To facilitate corrections due to
redshift, we include a sample of 288 galaxies with SDSS imaging that can be
transformed to simulate \hst{} imaging out to $z = 1$. 
The SDSS images were redshifted and processed to mimic simulated \hst{} imaging 
parameters using the \ferengi{} code \citep{bar08a}.

@@

In addition to the primary \hst{} legacy imaging sample with colored images
described as above, GZH also includes samples of \hst{} galaxy images with
different color prescriptions. In particular, there are 2 sets of 3,927 images
each, drawn from the COSMOS sample; the first has a dramatically reduced color
saturation, and the second has reversed the colors so that the blue and red
filters have exchanged places in the RGB image. The `faded' galaxy set
facilitates measuring of possible variations in classification due to the
presence or absence of color features. The `recolored' set enables an
alternative test of potential color biases in classifications.
% I guess this means we need to say somewhere later that we don't see an effect
% (we don't, right?).  Would also be good to cite here where we have done
% similar things in the past...

@@

%\ref{tbl:catalog_hst}
\item \main: \hst{} imaging with RGB colors making use of all available
filters with typical saturation and in correct order, as described in
Section~\ref{ssec:images}. This sample includes AEGIS, COSMOS, GEMS, and
full-depth GOODS (North and South) images. (118,425 galaxies)

%\ref{tbl:catalog_faded}
\item \faded: a subset of COSMOS images with very low color saturation.
(3,927 galaxies)

%\ref{tbl:catalog_recolored}
\item \recolored: a subset of COSMOS images with red and blue channels
reversed. Note: this sub-sample uses the same galaxies as the \texttt{faded}
sub-sample. (3,927 galaxies)

%\ref{tbl:catalog_goods_shallow}
\item \goods: Images from GOODS-North and GOODS-South, with
color from 2 filters and imaged at 2-epoch depth. (6,144 galaxies)

%\ref{tbl:stripe82_single}
\item \stripe: Single-epoch images from SDSS Stripe~82.
(21,522 galaxies)

%\ref{tbl:stripe82_coadd}
\item \coadd: Co-added images from SDSS Stripe~82. Note: this
sub-sample includes all galaxies in the \texttt{stripe-82-single} sub-sample,
with additional sources detected in the deeper imaging. (30,339 galaxies)

%ferengi <-- no table?
\item \redshifted: Simulated \hst{} images constructed using SDSS
images and artificially redshifted to between $0.3 \leq z \leq 1$. (288
original galaxies; 3,950 redshifted galaxies)

%\ref{tbl:simulated_agn}
\item \simagn: Simulated AGN host galaxies constructed using
\hst{} images and PSFs. (96 original galaxies; 2,961 simulated AGN host
galaxies)

@@

Photometric data for the bulk of the GZH \main, \faded, \recolored, and \goods{}
samples were largely drawn from the tables in \citet{gri12}. This included
photometric parameters such as the fluxes, magnitudes, radii, ellipticities,
position angles, and positions drawn from both \sextractor{} and \galfit.
\galfit{} also provided the parametric \sersic{} index and effective half-light
radius for the best-fit model. All parameters were measured in both bands of
the ACS imaging, with the exception of the single-band COSMOS images.

@@

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{figures/p_vs_p_SB_redshift.pdf}
\caption{Effects of redshift bias in 3,950 images in the \ferengi{} sample.
Each point \emph{in a given redshift and surface brightness bin} represents a
unique galaxy. On the $y$-axis in each bin is the \ffeatures{} value of the
image of that galaxy redshifted to the value corresponding to that redshift
bin. On the $x$-axis is the \ffeatures{} value of the image of the same galaxy
redshifted to $z=0.3$. The dashed black lines represent the best-fit
polynomials to the data in each square. The solid black line represents
\ffeaturesz=\ffeaturesrest. Regions in which there is a single-valued
relationship between \ffeatures{} at high redshift and at $z=0.3$ are white;
those in which there is not are blue, and those with not enough data ($N<5$)
are gray. A larger version of the bin outlined at $z=1.0$ and $20.3 < \mu <
21.0$ $\rm (mag/arcsec^2)$ is shown in Figure~\ref{fig:f_vs_f_zoom}.}
\label{fig:f_vs_f}
\end{figure*}

@@

The criteria for determining whether a region of this space is single-valued,
and therefore correctable, is as follows: In each surface brightness and
redshift bin, the relationship between \ffeaturesz{} and \ffeaturesrest{} is
modeled by fitting the data with polynomials of degrees $n=3$, 2, and 1, and
using the best formal fit out of the three as measured by the sum of the
residuals. These fits are shown as the dashed black lines in
Figure~\ref{fig:f_vs_f}. Flat regions of the bins are areas in which there is
not a clear single-valued relationship between \ffeaturesz{} and
\ffeaturesrest. We quantify this by measuring the slope of the best-fit
polynomical; regions of the bins with a slope less than 0.4 value are
considered \emph{not} one-to-one, and therefore \ffeaturesz{} cannot be boosted
to its \ffeaturesrest{} value.  Galaxies in this region are referred to as the
\emph{lower limit} sample, because the most stringent correction available is
that the weighted \ffeatures{} is a lower limit to the true value.  These
regions are highlighted in blue in Figure~\ref{fig:f_vs_f}. Uncolored (white)
regions of the plot have sufficiently high slopes to consider the relationship
as single-valued; galaxies in these regions are considered ``correctable'', and
only these are used in measuring the parameters for the $\zeta$ function
(Section~\ref{ssec:zeta}). Only surface brightness/redshift bins with at least
5 galaxies were considered; regions with fewer than 5 galaxies are considered
to have ``not enough information'' to determine the \ffeaturesz{} and
\ffeaturesrest{} relationship, colored gray in Figure~\ref{fig:f_vs_f}.

@@

For galaxies identified as ``clumpy'' in GZH, the number of clumps can be
determined using Task~16. Table~\ref{tbl:thresholds} can be used to select
8,444 galaxies measured as ``clumpy'' using \ffeatures$> 0.23$ and $f_{\rm
clumpy,yes}>0.80$ to ensure the vote fractions for Task~16 are well-sampled.
The clump number can be reasonably identified for 1,112 of the clumpy galaxies;
for the remainder, the unique clumps were less distinguishable from each other
and the exact number of clumps could not be deduced without careful visual
inspection. In the 1,112 which did have distinguishable clumps, there are
61 one-clump galaxies using $f_{\rm 1~clump}>0.50$, 442 two-clump galaxies
using $f_{\rm 2~clumps}>0.80$, 275 three-clump galaxies using $f_{\rm
3~clumps}>0.75$, 71 four-clump galaxies using $f_{\rm 4~clumps} > 0.70$,
and 263 galaxies with more than four clumps using $f_{\rm >4~clumps}>0.70$.
Alternatively, these data may be used to create more general samples of
clumpy galaxies with few clumps and many clumps. A sample of 989 ``few
clumps'' galaxies can be made using $(f_{\rm 1~clump} + f_{\rm 2~clumps}) >
0.5$ and 2,910 ``many clumps'' galaxies using $(f_{\rm 3~clumps}+f_{\rm
4~clumps}+f_{\rm >4~clumps})>0.5$.

@@

The types and accuracy of morphological classification strongly depend on the
sample and methods being used. In an attempt to make a consistent comparison
between different techniques, galaxies are broadly grouped into three
categories: bulge-dominated/elliptical/smooth, disk-dominated/spiral, and
irregular/clumpy. These categories are compared to two parameters in GZH:
\fbest, which is designed to identify smooth (elliptical) galaxies, and \fodd,
which is designed to identify deviations from well-formed spirals or S0s and
which constitutes a ``catch-all'' for the variety of asymmetric morphologies
that can constitute an irregular galaxy.

@@

AEGIS galaxies were morphologically classified using non-parametric
measurements by \citet{lot08}. This method used a combination of the Gini
coefficient ($G$), which measures the relative inequality in pixel brightness,
and $M_{20}$, the second-order moment of the brightest 20\% of the light
\citep{lot04}. A linear combination of $G$ and $M_{20}$ delineates three broad
categories of galaxy morphology: E/S0/Sa (``elliptical''), Sb/Sc/Ir
(``spiral''), and mergers (``irregular''). A 1\arcsec{} positional match on
AEGIS and GZH yields 4,031 galaxies with reliably-measured morphologies and
$S/N>3$ in both $V$- and $I$-bands.

Galaxies in both of the GOODS fields down to a limit of $z_{AB}=22.5$ were
visually classified by a single expert (R.S.~Ellis), inspecting both $z$-band
and composite $Viz$ color images \citep{bun05}. These morphologies are assigned
a numerical value based on categories in \citet{bri98a}: the corresponding
morphologies used are ``elliptical'' (classes 0,1,2), ``spirals'' (classes
3,4,5), and ``irregular'' (classes 6,7,8). A 0.5\arcsec{} matched radius yields
2,435 galaxies (1300 in GOODS-N, 1135 in GOODS-S) in both \citet{bun05} and
GZH.

COSMOS galaxies have multiple published datasets automatically classifying
morphology, all using a variation of non-parametric measurements. \citet{cas07}
used a combination of concentration ($C$), asymmetry ($A$), $G$, and $M_{20}$
\citep{cas05} to classify all galaxies with $m_\mathrm{I,petro}<25$, and used
an empirical division based on several hundred training images to assign
galaxies to discrete morphological categories. A similar method is employed by
\citet{tas11}, using the same non-parametric indices but with a different
method of calculating the Petrosian radius and total light profile. They employ
a nearest-neighbors method to assign morphological categories for the
entire sample based on a small training set. \citet[][ZEST]{sca07} used $C$,
$A$, $G$, $M_{20}$, the galaxy ellipticity ($\epsilon$), and \sersic{} index
($n$) to quantify the galaxy shapes; a principal component analysis is used to
assign galaxies to discrete morphological categories. The categories in all
three methods are split into ellipticals, spirals, and peculiar/irregulars. A
0.5\arcsec{} radius search on GZH matches to 76,241 galaxies in \citet{cas07},
76,608 in \citet{tas11}, and 77,425 in \citet{sca07}.

\begin{figure*}
\center
\includegraphics[width=1.0\textwidth]{figures/comparisons.png}
\caption{Distributions of morphological parameters for galaxies matched in GZH
and other published catalogs, split by survey (AEGIS, COSMOS, GEMS, and GOODS).
The first and third columns show the fraction of overall galaxies in the
matched samples, split by their published morphologies as a function of the GZH
\fbest. The corresponding second and fourth columns show data for the same
galaxies as a function of \fodd. The ``odd'' samples exclude galaxies dominated
by lenses or dust lanes ($<1\%$ of the total), which are GZH categories not
expected to correlate to larger-scale structural parameters. Confidence
intervals for each binned fraction in the bin are calculated for a binomial
population \citep{cam11}.}
\label{fig:comparisons}
\end{figure*}

@@

This paper presents the catalog release for the Galaxy Zoo: Hubble project,
which uses crowdsourced visual classifications to measure galaxy morphologies.
The first two phases of Galaxy Zoo \citep{lin11,wil13} used images of
low-redshift galaxies from SDSS; this is the first result of the project with
space-based images of high-redshift targets (in addition to the Galaxy Zoo:
CANDELS collaboration; Simmons et al., submitted). The final sample includes
classifications for 181,101~images generated from 150,771~unique galaxies.
Galaxies were selected from a brightness-limited sample from multiple Legacy
surveys using the Advanced Camera for Surveys on the Hubble Space Telescope,
including AEGIS, GEMS, GOODS-N, GOODS-S, and COSMOS. The catalog also includes
classifications for 51,861 SDSS images from Stripe~82 at
relatively low redshift; these serve both as a low-redshift anchor for
cosmological studies and a potential comparison for the different epochs of
classification between GZH and Galaxy Zoo 2 \citep{wil13}.

>>>>

\item The Great Observatories Origins Deep Survey \citep[GOODS;][]{gia04}
    covered two separate fields in the northern and southern hemispheres: the Hubble
    Deep Field-North ($\alpha=12^\textrm{h}36^\textrm{m},
    \delta=+62^\circ14^\prime$) and the Chandra Deep Field-South
    ($\alpha=03^\textrm{h}32^\textrm{m}, \delta=-27^\circ48^\prime$). The \hst{}
    ACS imaging data from the two fields are referred to as GOODS-N and GOODS-S,
    respectively. ACS imaging in GOODS fields used 4~filters -- F435W (\Bband),
    \Vband, F775W (\iband), and F850LP (\zband). The mean exposure times for each
    epoch varied by band, from 1050--2100~seconds. The \Bband{} images were completed
    in a single epoch at the beginning of the survey, but the \Vband, \iband, and
    \zband{} images were taken in five separate epochs separated by 40--50~days
    each. Images were dithered to a pixel scale of 0.03~\arcsec/pixel and covered a
    total area of $\sim320$~arcmin$^2$ (160~arcmin$^2$ per north/south field). The
    $5\sigma$ limiting magnitude for extended sources was 25.7 for \Vband{} and
    25.0 for \iband.

\item The Cosmic Evolution Survey \citep[COSMOS;][]{sco07} covered an area of
    $\sim1.8$~deg$^2$ centered at $\alpha=10^\textrm{h}00^\textrm{m},
    \delta=+02^\circ12^\prime$. Its location near the celestial equator was
    designed to enable coverage by ground-based telescopes in both the Northern and
    Southern Hemispheres, in addition to space-based observatories. The ACS data
    for COSMOS consisted of 1~orbit per pointing with an exposure time of
    2028~seconds in \Iband; 590~total pointings were used to cover the entire
    field. The image resolution was dithered to 0.05~\arcsec/pixel. The 50\%
    completeness magnitude for a galaxy with a half-light radius of
    $0.50^{\prime\prime}$ in \Iband{} was 24.7~mag.

\item The Galaxy Evolution from Morphologies and SEDs
    \citep[GEMS;][]{rix04,cal08} survey was also centered on the Chandra Deep
    Field-South. The GEMS data covered $\sim800$~arcmin$^2$, completely surrounding
    the area covered by GOODS-S. Images from ACS in GEMS had 1~orbit per pointing
    for a total of 63~pointings. The exposure times were 2160 and 2286~seconds in
    \Vband{} and \zband{}, respectively. The image resolution had a pixel scale
    of 0.03~\arcsec/pixel. The $5\sigma$ limiting magnitude for source
    detection was 25.7~AB in \Vband{} and 24.2~AB in \zband.

@@

%The creation of 51,861 images from these sources is described in Section
%\ref{ssec:galselect} below.
Single-epoch images from SDSS Stripe~82 were selected using the criteria
from \citet{wil13}, which required limits of \texttt{petroR90\_r}$ >
3$\arcsec~(where \texttt{petroR90\_r} is the radius containing 90\% of the
$r^\prime$ Petrosian flux) and a magnitude brighter than $m_r < 17.77$. The
images used were three-color composites created using the $g^\prime$, $r^\prime$, and
$i^\prime$ filters \citep{nie04}. 21,522~galaxies in SDSS met these criteria.
Co-added images from Stripe~82 were selected from the union of galaxies with
co-added magnitudes brighter than $17.77$~mag, and the galaxies detected in the
\stripe{} images and matched to a co-add source. This resulted in a total
set of 30,339~images. Of the images in the co-added sample, 5144 (17~percent)
were dimmer than the initial magnitude cut of 17.77.

@@

Two sets of simulated AGN were generated in GZH. The first set (version~1) was
assembled from 95~galaxies from GOODS-S imaging and empirical PSFs made by
combining stars in the GOODS fields using the PSF creation tools in
\texttt{daophot}.  The second set (version~2) was assembled from 96~galaxies in
GOODS-S; this version used simulated PSFs from \texttt{TinyTim} \citep{kri93},
drizzled using the same procedures as those used in the reduction of the GOODS-S
images \citep{koe02,koe03,gia04}. The use of these two versions facilitates
comparisons between these different PSF creation methods, which are widely used
in AGN host galaxy morphology studies
\citep[e.g.,][]{san04,sim08,pie10a,simm11}.  Each PSF creation method has
advantages and disadvantages: the empirical PSFs better represent the nuances
of the PSF in the specific data being used and look more realistic at lower
luminosities, but the extended features of the noiseless \texttt{TinyTim} PSFs
are visually more realistic at higher luminosities.
% okay so I'm a cheeky self-citing biyotch

@@

The dimming and resolution effects of redshift can significantly affect galaxy
classifications derived from any method. To facilitate corrections due to
redshift, we include a sample of 288~galaxies with SDSS imaging that can be
transformed to simulate \hst{} imaging out to $z = 1$. 
The SDSS images were redshifted and processed to mimic simulated \hst{} imaging 
parameters using the \ferengi{} code \citep{bar08a}.

@@

In addition to the primary \hst{} legacy imaging sample with colored images
described as above, GZH also includes samples of \hst{} galaxy images with
different color prescriptions. In particular, there are two sets of 3,927~images
each, drawn from the COSMOS sample; the first has a dramatically reduced color
saturation, and the second has reversed the colors so that the blue and red
filters have exchanged places in the RGB image. The `faded' galaxy set
facilitates measuring of possible variations in classification due to the
presence or absence of color features. The `recolored' set enables an
alternative test of potential color biases in classifications.
% I guess this means we need to say somewhere later that we don't see an effect
% (we don't, right?).  Would also be good to cite here where we have done
% similar things in the past...

@@

%\ref{tbl:catalog_hst}
\item \main: \hst{} imaging with RGB colors making use of all available
filters with typical saturation and in correct order, as described in
Section~\ref{ssec:images}. This sample includes AEGIS, COSMOS, GEMS, and
full-depth GOODS (North and South) images. (118,425~galaxies)

%\ref{tbl:catalog_faded}
\item \faded: a subset of COSMOS images with very low color saturation.
(3,927~galaxies)

%\ref{tbl:catalog_recolored}
\item \recolored: a subset of COSMOS images with red and blue channels
reversed. Note: this sub-sample uses the same galaxies as the \texttt{faded}
sub-sample. (3,927~galaxies)

%\ref{tbl:catalog_goods_shallow}
\item \goods: Images from GOODS-North and GOODS-South, with
color from 2~filters and imaged at 2-epoch depth. (6,144~galaxies)

%\ref{tbl:stripe82_single}
\item \stripe: Single-epoch images from SDSS Stripe~82.
(21,522~galaxies)

%\ref{tbl:stripe82_coadd}
\item \coadd: Co-added images from SDSS Stripe~82. Note: this
sub-sample includes all galaxies in the \texttt{stripe-82-single} sub-sample,
with additional sources detected in the deeper imaging. (30,339~galaxies)

%ferengi <-- no table?
\item \redshifted: Simulated \hst{} images constructed using SDSS
images and artificially redshifted to between $0.3 \leq z \leq 1$. (288
original galaxies; 3,950~redshifted galaxies)

%\ref{tbl:simulated_agn}
\item \simagn: Simulated AGN host galaxies constructed using
\hst{} images and PSFs. (96~original galaxies; 2,961~simulated AGN host
galaxies)

@@

Photometric data for the bulk of the GZH \main, \faded, \recolored, and
\goods{} samples were largely drawn from the tables in \citet{gri12}. This
included photometric parameters such as the fluxes, magnitudes, radii,
ellipticities, position angles, and positions drawn from both \sextractor{} and
\galfit.  All photometric parameters were measured in both bands of the ACS
imaging, with the exception of the single-band COSMOS images. Photometric data
for the GOODS 5-epoch imaging, including \sextractor{} parameters, is from
\citet{gia12}.
%\galfit{} also provided the parametric \sersic{} index and effective
%half-light radius for the best-fit model.

@@

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{figures/p_vs_p_SB_redshift.pdf}
\caption{Effects of redshift bias in 3,950~images in the \ferengi{} sample.
Each point \emph{in a given redshift and surface brightness bin} represents a
unique galaxy. On the $y$-axis in each bin is the \ffeatures{} value of the
image of that galaxy redshifted to the value corresponding to that redshift
bin. On the $x$-axis is the \ffeatures{} value of the image of the same galaxy
redshifted to $z=0.3$. The dashed black lines represent the best-fit
polynomials to the data in each square. The solid black line represents
\ffeaturesz=\ffeaturesrest. Regions in which there is a single-valued
relationship between \ffeatures{} at high redshift and at $z=0.3$ are white;
those in which there is not are blue, and those with not enough data ($N<5$)
are gray. A larger version of the bin outlined at $z=1.0$ and $20.3 < \mu <
21.0$ $\rm (mag/arcsec^2)$ is shown in Figure~\ref{fig:f_vs_f_zoom}.}
\label{fig:f_vs_f}
\end{figure*}

@@

The criteria for determining whether a region of this space is single-valued,
and therefore correctable, is as follows: In each surface brightness and
redshift bin, the relationship between \ffeaturesz{} and \ffeaturesrest{} is
modeled by fitting the data with polynomials of degrees $n=3$, 2, and 1, and
using the best formal fit out of the three as measured by the sum of the
residuals. These fits are shown as the dashed black lines in
Figure~\ref{fig:f_vs_f}. Flat regions of the bins are areas in which there is
not a clear single-valued relationship between \ffeaturesz{} and
\ffeaturesrest. We quantify this by measuring the slope of the best-fit
polynomical; regions of the bins with a slope less than 0.4 are
considered \emph{not} one-to-one, and therefore \ffeaturesz{} cannot be boosted
to its \ffeaturesrest{} value.  Galaxies in this region are referred to as the
\emph{lower limit} sample, because the most stringent correction available is
that the weighted \ffeatures{} is a lower limit to the true value.  These
regions are highlighted in blue in Figure~\ref{fig:f_vs_f}. Uncolored (white)
regions of the plot have sufficiently high slopes to consider the relationship
as single-valued; galaxies in these regions are considered ``correctable'', and
only these are used in measuring the parameters for the $\zeta$ function
(Section~\ref{ssec:zeta}). Only surface brightness/redshift bins with at least
5~galaxies were considered; regions with fewer than 5~galaxies are considered
to have ``not enough information'' to determine the \ffeaturesz{} and
\ffeaturesrest{} relationship, colored gray in Figure~\ref{fig:f_vs_f}.

@@

For galaxies identified as ``clumpy'' in GZH, the number of clumps can be
determined using Task~16. Table~\ref{tbl:thresholds} can be used to select
8,444~galaxies measured as ``clumpy'' using \ffeatures$> 0.23$ and $f_{\rm
clumpy,yes}>0.80$ to ensure the vote fractions for Task~16 are well-sampled.
The clump number can be reasonably identified for 1,112 of the clumpy galaxies;
for the remainder, the unique clumps were less distinguishable from each other
and the exact number of clumps could not be deduced without careful visual
inspection. In the 1,112 which did have distinguishable clumps, there are
61 one-clump galaxies using $f_{\rm 1~clump}>0.50$, 442 two-clump galaxies
using $f_{\rm 2~clumps}>0.80$, 275 three-clump galaxies using $f_{\rm
3~clumps}>0.75$, 71 four-clump galaxies using $f_{\rm 4~clumps} > 0.70$,
and 263~galaxies with more than four clumps using $f_{\rm >4~clumps}>0.70$.
Alternatively, these data may be used to create more general samples of
clumpy galaxies with few clumps and many clumps. A sample of 989 ``few
clumps'' galaxies can be made using $(f_{\rm 1~clump} + f_{\rm 2~clumps}) >
0.5$ and 2,910 ``many clumps'' galaxies using $(f_{\rm 3~clumps}+f_{\rm
4~clumps}+f_{\rm >4~clumps})>0.5$.

@@

The types and accuracy of morphological classification strongly depend on the
sample and methods being used. In an attempt to make a consistent comparison
between different techniques, galaxies are broadly grouped into three
categories: bulge-dominated/elliptical/smooth, disk-dominated/spiral, and
irregular/clumpy. These categories are compared to two parameters in GZH:
\fbest, which identifies disk-dominated and clumpy galaxies, and \fodd,
which identifies deviations from well-formed spirals or S0s and
which constitutes a ``catch-all'' for the variety of asymmetric morphologies
that can constitute an irregular galaxy.

@@

AEGIS galaxies were morphologically classified using non-parametric
measurements by \citet{lot08}. This method used a combination of the Gini
coefficient ($G$), which measures the relative inequality in pixel brightness,
and $M_{20}$, the second-order moment of the brightest 20\% of the light
\citep{lot04}. A linear combination of $G$ and $M_{20}$ delineates three broad
categories of galaxy morphology: E/S0/Sa (``elliptical''), Sb/Sc/Ir
(``spiral''), and mergers (``irregular''). A 1\arcsec{} positional match on
AEGIS and GZH yields 4,031~galaxies with reliably-measured morphologies and
$S/N>3$ in both $V$- and $I$-bands.

Galaxies in both of the GOODS fields down to a limit of $z_{AB}=22.5$ were
visually classified by a single expert (R.S.~Ellis), inspecting both $z$-band
and composite $Viz$ color images \citep{bun05}. These morphologies are assigned
a numerical value based on categories in \citet{bri98a}: the corresponding
morphologies used are ``elliptical'' (classes 0,1,2), ``spirals'' (classes
3,4,5), and ``irregular'' (classes 6,7,8). A 0.5\arcsec{} matched radius yields
2,435~galaxies (1300 in GOODS-N, 1135 in GOODS-S) in both \citet{bun05} and
GZH.

COSMOS galaxies have multiple published datasets automatically classifying
morphology, all using a variation of non-parametric measurements. \citet{cas07}
used a combination of concentration ($C$), asymmetry ($A$), $G$, and $M_{20}$
\citep{cas05} to classify all galaxies with $m_\mathrm{I,petro}<25$, and used
an empirical division based on several hundred training images to assign
galaxies to discrete morphological categories. A similar method is employed by
\citet{tas11}, using the same non-parametric indices but with a different
method of calculating the Petrosian radius and total light profile. They employ
a nearest-neighbors method to assign morphological categories for the
entire sample based on a small training set. \citet[][ZEST]{sca07} used $C$,
$A$, $G$, $M_{20}$, the galaxy ellipticity ($\epsilon$), and \sersic{} index
($n$) to quantify the galaxy shapes; a principal component analysis is used to
assign galaxies to discrete morphological categories. The categories in all
three methods are split into ellipticals, spirals, and peculiar/irregulars. A
0.5\arcsec{} radius search on GZH matches to 76,241~galaxies in \citet{cas07},
76,608 in \citet{tas11}, and 77,425 in \citet{sca07}.

\begin{figure*}
\center
\includegraphics[width=1.0\textwidth]{figures/comparisons.pdf}
\caption{Distributions of morphological parameters for galaxies matched in GZH
and other published catalogs, split by survey (AEGIS, COSMOS, GEMS, and GOODS).
The first and third columns show the fraction of overall galaxies in the
matched samples, split by their published morphologies as a function of the GZH
\fbest. The corresponding second and fourth columns show data for the same
galaxies as a function of \fodd. The ``odd'' samples exclude galaxies dominated
by lenses or dust lanes ($<1\%$ of the total), which are GZH categories not
expected to correlate to larger-scale structural parameters. Confidence
intervals for each binned fraction in the bin are calculated for a binomial
population \citep{cam11}.}
\label{fig:comparisons}
\end{figure*}

@@

This paper presents the catalog release for the Galaxy Zoo: Hubble project,
which uses crowdsourced visual classifications to measure galaxy morphologies.
The first two phases of Galaxy Zoo \citep{lin11,wil13} used images of
low-redshift galaxies from SDSS; this is the first result of the project with
space-based images of high-redshift targets (in addition to the Galaxy Zoo:
CANDELS collaboration; Simmons et al., submitted). The final sample includes
classifications for 181,101~images generated from 150,771~unique galaxies.
Galaxies were selected from a brightness-limited sample from multiple Legacy
surveys using the Advanced Camera for Surveys on the Hubble Space Telescope,
including AEGIS, GEMS, GOODS-N, GOODS-S, and COSMOS. The catalog also includes
classifications for 51,861~SDSS images from Stripe~82 at
relatively low redshift; these serve both as a low-redshift anchor for
cosmological studies and a potential comparison for the different epochs of
classification between GZH and Galaxy Zoo 2 \citep{wil13}.
